---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# RILStEp

<!-- badges: start -->
<!-- badges: end -->
RILStEp(Recombinant Inbred Lines Stepwise Epistasis analysis) package is the epistasis analysis tool.
This package enables to detect the epistatic relationships between SNPs for RIL population by comparison of 2 models based on bayes factor.<br>
first model  : only QTL effects.
second model : QTL effects & epistasis effects.

## Installation

You can install RILStEp from [GitHub](https://github.com/slt666666/RILStEp) with:

``` r
# install.packages("devtools")
devtools::install_github("slt666666/RILStEp")
```
## Example

This is a basic example script:

```{r example, eval = FALSE}
library(RILStEp)

### loading dataset
loaded_data <- load_data("phenotype.csv", "genotype.csv", "trait1")

### check all combinations of 2 SNPs
result1 <- rilstep(loaded_data, "result1", core_num = 8)

### using 1 SNP in each 500 SNPs
result2 <- rilstep(loaded_data, "result2", interval = 500)

### specify QTL-like SNPs by user.
result3 <- rilstep(loaded_data, "result3", qtls = c("chr08_19928351", "chr09_3909046"))

### using SNPs in specific regions
result4 <- rilstep(loaded_data, "result4", regions = c("chr03_2132221:chr10_9330401", "chr03_2132221:chr10_9330401"))
```
option `region=c()` can specify regions. rilstep check all combinations of SNPs in specified regions.
```
regions = c("chr03_1234")                                    # chr03_1234 x all SNPs
regions = c("chr03_1234:chr10_5678")                         # chr03_1234 ~ chr10_5678 x all SNPs
regions = c("chr03_1234", "chr10_5678")                      # chr03_1234 x chr10_5678
regions = c("chr03_1234:chr10_5678", "chr04_9012:chr7_3456") # chr03_1234~chr10_5678 x chr04_9012~chr7_3456
```
